### 2017-12-24 icde/revision/Response.tex

\documentclass{letter}
\usepackage{geometry}

% duan
\usepackage{xspace}

\geometry{left=2.0cm, right=2.0cm, top=2.5cm, bottom=2.5cm}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\aka}{\emph{a.k.a.}\xspace}
\newcommand{\kwlog}{\emph{w.l.o.g.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\sstab}{\rule{0pt}{8pt}\\[-2.4ex]}

\begin{document}

Prof. xxx,\\
Editor-in-Chief,\\
%IEEE Transactions on Knowledge and Data Engineering\\

Dear Prof. xxx,

%Attached please find a revised version of our submission to IEEE Transactions on Knowledge and Data Engineering, \emph{An Ensemble Approach to Link Prediction}.

%The paper has been substantially revised according to the referees＊ comments. In particular, (1) we have added an example to explain the procedure of the top-$(\epsilon, k)$ prediction, (2) we have compared the suggested Resource Allocation (RA) algorithm in the experimental study, (3) we have added an accuracy comparison with varied hop distances of our methods and BIGCLAM in the experimental study, (4) we have compared our methods with the state-of-the-art methods when $k$ is fixed to the number of links in the ground truth data and reported the accuracy results together with the 95\% confidence intervals in Appendixes A\&B of the supplementary material for the lack of space, (5) we have implemented and evaluated the ensemble-enabled approach with Adamic/Adar (AA) and RA in Appendix C of the supplementary material, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.

We would like to thank all the referees for their thorough reading of our paper and for their valuable comments.

Below please find our responses to the comments by the referees.

%******************* reviewer 1 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 1.}

\textbf{[R1W1]} \emph{Formula 7 in SARank still needs parameters, which are not easy to set.}

We have added this survey in the related work (Section 5). Thanks!

\textbf{[R1W2]} \emph{The extension of this method to query dependent ranking or other heterogeneous information network should be discussed.}

Yes, we have discussed the complexities of AA and RA when we introduce them in Section 4.1. Moreover, $O(n^2)$ typically refers to the number of possible links in our paper.

\textbf{[R1D1]} \emph{In the time-weighted pagerank algorithm, the impacts are encoded into the edge weight. How about changing the values on nodes?}

We have added Example 1 (Section 2.1) to illustrate the procedure for
top-$(\epsilon, k)$ prediction searching. Thanks for the suggestion!

\textbf{[R1D2]} \emph{This paper has an important observation that ※the impact of an article tends to decay with time after the peak time only.§ However, I cannot see that from Figure 1. It is better to add some references to support the claim.}

We have explained the setting of the parameter $\theta$ in the second last paragraph of Section 3.6, and removed Proposition 2. Thanks for the suggestion!

\textbf{[R1D3]} \emph{How to determine the peak time for the PeakMul pattern?}

The snowball sampling has been introduced in the graph sampling
survey [4] in our references. Indeed, the edge bagging method
is different from the snowball sampling because the edge bagging only
selects a random adjacent node when the sampled node set is growing.
Hence, we did not cite the recommended paper directly due to space limitations (as you may notice, we already provide a supplementary material).  Thanks!

[4] N. K. Ahmed, J. Neville, and R. Kompella. Network sampling: From
static to streaming graphs. Transactions on Knowledge Discovery from
Data (TKDD), 8(2):7:1每7:56, 2014.

\textbf{[R1D4]} \emph{For large scholar graph, such as MAG, it is better to use the distributed graph processing framework to improve the scalability of the method}

We focus on predicting future links that split by timestamps (the datasets that we used have timestamps of edge arrivals) rather than missing links
that selected randomly from the network as the testing set [17][24]. Hence, we believe these methods are not comparable.

\textbf{[R1D5]} \emph{TWPageRank works better on the scholar graphs than the general web graph. is it due to that the citation graph is an directed acyclic graph?}

We have added
the link predictability work [30] in the related work (Section 5), and the survey papers [17]\&[31].

[17] M. A. Hasan and M. J. Zaki. A survey of link prediction in social
networks. In Social Network Data Analytics, 2011.

[30] L. L\"{u}, L. Pan, T. Zhou, Y. Zhang, and H. Stanley. Toward link
predictablility of complex networks. PNAS, 118(8):2325每2330, 2015.

[31] L. L\"{u} and T. Zhou. Link prediction in complex networks: A survey.
Physica A, pages 1150每1170, 2011.

\textbf{[R1D6]} \emph{MAG is used before description in Page 1.
Some cells in Table 1 have two values, while others have one value. The meaning should be given explicitly}

Yes, we have added RA as a comparison algorithm in the experimental study. However,
we did not adopt the other algorithms for comparison since the complexities of these
algorithms are at least $O(n^2)$ and they cannot work on large
networks with millions of nodes. Thanks for the suggestion!

%******************* reviewer 2 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.}

We have added the accuracy test with the 95\% confidence intervals when $k$ is fixed
to its default value and the number of links in the ground truth data (R2C2).
Due to space limitations, we choose to report these experimental results in the Appendix B
of the supplementary material, in which the results justify the effectiveness of our methods compared with the state-of-the-art methods.
Thanks for the suggestion!

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

We agree that small changes of the value $k$ may lead to different conclusions.
This is why we tested the impact of varying $k$ in the experimental study.

Similar to [35][39] that do not use the number of links in the
ground truth data for testing accuracy, we keep the results using default values for $k$ in the experimental study.
However, we further tested the ensemble-enabled approach with $k$ fixed to the number of links in
the ground truth data. Due to space limitations, we choose to report these experimental results in the Appendix A
of the supplementary material, in which the results justify the effectiveness and efficiency of our methods compared with the state-of-the-art methods.
Thanks for the suggestion!

It is worth mentioning that the datasets used in our experiments
are more much sparser than the one used in [S1], which means that it
is more difficult to predict links on our datasets. As a result, the top-$k$
precision on our datasets, when $k$ is fixed to the number of links in the
ground truth data, is too low to be useful in practice.

[S1] Y. Yang, R. N. Lichtenwalter, and N. V. Chawla. Evaluating link prediction
methods. Knowl Inf Syst, 45:751每782, 2015.

[35] D. Song, D. Meyer, and D. Tao. Top-k link recommendation in social
networks. In ICDM, 2015.

[39] R. West, A. Paranjape, and J. Leskovec. Mining missing hyperlinks from
human navigation traces: A case study of wikipedia. In WWW, 2015.

\textbf{[R2D1]} \emph{There seem to be two "contradictory" sides to this paper. From one side, this is a great "applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that "Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We have added an accuracy comparison of our methods and
BIGCLAM with varied hop distances in Section 4.2.4. The results show
that all these methods are more accurate in predicting 2 or 3 hop distance
links, and they are not good at predicting links with large hop distances.
This is a general limitation of most (if not all) existing methods, which deserves  a full treatment in the future.

Thanks for helping us to identify the limitation of our method!

\textbf{[R2D2]} \emph{The abstract starts with the sentence "Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really "critical".}

We have added a remark in the end of Section 3.6 such that our ensemble-enabled approach
is a general method for decomposing the large network link prediction
problem into smaller subproblems, which is not limited to NMF, and may be applied to other link prediction methods such as AA and RA.

We have revised the bagging+ and bagging methods by replacing NMF with AA and RA, respectively, and  we evaluated and reported their performance
in the Appendix C of the supplementary material. Our preliminary results indeed show that the
ensemble-enabled AA and RA are very promising, though more sophisticated sampling techniques are needed for achieving better performances.  Thanks for this great comment!

\textbf{[R2D3]} \emph{On page 4, you say "However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle "on a PC with 2 Intel Xeon E5每2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

%******************* reviewer 3 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 3.}

\textbf{[R3C1]} \emph{The section could be preceded by clearly noting
the two challenges (prediction/training complexity) in large networks,
and how separate tools are used to handle each.}

The parameters are designed to fit variety ranking with different demands. For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component. Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.

\line(1,0){500}

Your sincerely,

Shuai Ma, Chen Gong, Renjun Hu, Dongsheng Luo, Chunming Hu, Jinpeng Huai

\end{document}

### 2017-12-24 icde/revision/Response.tex

Prof. xxx,\\
Editor-in-Chief,\\
%IEEE Transactions on Knowledge and Data Engineering\\

Dear Prof. xxx,

%Attached please find a revised version of our submission to IEEE Transactions on Knowledge and Data Engineering, \emph{An Ensemble Approach to Link Prediction}.

%The paper has been substantially revised according to the referees¡¯ comments. In particular, (1) we have added an example to explain the procedure of the top-$(\epsilon, k)$ prediction, (2) we have compared the suggested Resource Allocation (RA) algorithm in the experimental study, (3) we have added an accuracy comparison with varied hop distances of our methods and BIGCLAM in the experimental study, (4) we have compared our methods with the state-of-the-art methods when $k$ is fixed to the number of links in the ground truth data and reported the accuracy results together with the 95\% confidence intervals in Appendixes A\&B of the supplementary material for the lack of space, (5) we have implemented and evaluated the ensemble-enabled approach with Adamic/Adar (AA) and RA in Appendix C of the supplementary material, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.

@@

\textbf{[R1W1]} \emph{Formula 7 in SARank still needs parameters, which are not easy to set.}

The parameters are designed to fit variety ranking with different demands. For example, the ground-truth RECOM prefer venue component while PFCTN prefer citation component. Furthermore, our parameters are quite flexible to choose in a certain range for suiting different ranking which we have discussed in Exp-4.3.

\textbf{[R1W2]} \emph{The extension of this method to query dependent ranking or other heterogeneous information network should be discussed.}

We focus on query independent ranking because of its application in Google Schorlar and MicroSoft Academic Search. As to extension of query dependent ranking, our ranking scores can combine with the relevance scores given a specific query. For other heterogeneous information network, the extension of our method is not known.

@@

\textbf{[R1D1]} \emph{In the time-weighted pagerank algorithm, the impacts are encoded into the edge weight. How about changing the values on nodes?}

Actually, changing the values on nodes is the key of our ranking method which evaluate the weight of nodes. Moreover, the change of nodes is difficult to handle due to the multiple iterations and probably cause the result fail to converge. To our knowledge, there is no related work on changing node weight and it is unclear how to change it. Finally, we set the weight of edges to achieve the change of impacts since they are essentially propagable in the network through edges.

\textbf{[R1D2]} \emph{This paper has an important observation that ¡°the impact of an article tends to decay with time after the peak time only.¡± However, I cannot see that from Figure 1. It is better to add some references to support the claim.}

Figure 1 shows the logscale number of citations grow exponentially with time, instead of impacts of individual articles.

@@

\textbf{[R1D3]} \emph{How to determine the peak time for the PeakMul pattern?}

The PeakMul pattern is defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years. In our work, we have simplified the pattern and only use the latest peak time which we have discussed in section II-A.

[19]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.

@@

\textbf{[R1D4]} \emph{For large scholar graph, such as MAG, it is better to use the distributed graph processing framework to improve the scalability of the method}

Yes, we agree that distributed processing is an important and independent problem which will be studied in future work and we have discussed it in Section VII. Thanks for the suggestion!

@@

\textbf{[R1D5]} \emph{TWPageRank works better on the scholar graphs than the general web graph. is it due to that the citation graph is an directed acyclic graph?}

Yes, but the citation graph does have cycles and is not a DAG. Compare to general web graphs, the computation of TWPageRank in scholarly graphs is more efficient as a result of the less SCC edge ratio which is shown in Table I. In addition, we have designed the incremental algorithm based on this feature of scholalry graphs and it works better.

@@

%******************* reviewer 2 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 2.}

\textbf{[R2W1]} \emph{While practically the paper makes a good case about the particular application domain and its contributions there, the paper lacks technical depth.}

We think that the techniques proposed also have their own interests: (1) An ensemble based ranking model itself is hard to define, (2) an incremental algorithm that makes use of the particular properties of the scholar graph, and (3) a through experimental study. That is, this paper certainly has its contributions to the technical part.

@@

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

Yes, we have gone over the paper and improved the presentation to make it more understandable. Thanks for the suggestion!

@@

\textbf{[R2D1]} \emph{There seem to be two "contradictory" sides to this paper. From one side, this is a great "applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that "Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We thank the reviewer for appreciating the practice merit of our work. And we believe this paper also stands from research and technique perspective: (1)

@@

\textbf{[R2D2]} \emph{The abstract starts with the sentence "Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really "critical".}

Yes, we have downgraded the tone and changed it into practical and difficult. Thanks for the suggestion!

\textbf{[R2D3]} \emph{On page 4, you say "However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle "on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

We have remove the sentence and explained the statement better. We have added the explanation of the generation of author citation graph and the size of the graph which makes it computationally expensive.

@@

%******************* reviewer 3 ***********************************************
\line(1,0){500}

\textbf{Response to the comments of Referee 3.}

\textbf{[R3W1\&D2]} \emph{More examples are suggested, especially when introducing the definitions, to make it easier for readers to understand.}

Yes, we agree that there should be more examples and add figures to illustrate how to generate components from scholarly data. However, due to the space limitation, we choose to report the examples in extended version.

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have added the report of the memory cost in experiment Exp-x.x by numbers instead of figures due to the space limitation.Thanks for the suggestion!

\textbf{[R3D1]} \emph{Although the authors have a detailed introduction about the growing data, detailed figures about the data are recommended in the introduction.}

We have added a figure x to show the volume statistics of the data.

\textbf{[R3D3]} \emph{It is suggested that the authors should include some references to papers addressing the time delaying problem such as temporal graph, since it is related to the topic.}

We have added citations [xx][yy] about time delaying problem and discussed it in Section VI Related Work.

### 2017-12-24 icde/revision/Response.tex

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

Yes, we have gone over the paper and improved the presentation to make it more understandable. Thanks for the suggestion!

\textbf{[R2D1]} \emph{There seem to be two "contradictory" sides to this paper. From one side, this is a great "applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that "Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We thank the reviewer for appreciating the practice merit of our work. And we believe this paper also stands from research and technique perspective: (1)  . We have further clarified our contributions in Section I Introduction and claimed the technique difference of our algorithm in Section VI Related Work.

@@

\textbf{[R2D2]} \emph{The abstract starts with the sentence "Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really "critical".}

Yes, we have downgraded the tone and changed it into practical and difficult. Thanks for the suggestion!

\textbf{[R2D3]} \emph{On page 4, you say "However, the resulting author citation graph to compute the prestige is typically too large to handle". This is a questionable statement. Maybe it is too large to handle "on a PC with 2 Intel Xeon E5¨C2630 2.4GHz CPUs and 64 GB of memory" but approaches like PageRank has been used for web-scale data so unless there is something that I am missing, this statement should also go (or explained better).}

We have removed the sentence and explained the statement better. We have added the explanation of the generation of author citation graph and the size of the graph which makes it computationally expensive.

### 2017-12-24 icde/revision/Response.tex

% duan
\usepackage{xspace}

\geometry{left=2.0cm, right=2.0cm, top=2.5cm, bottom=2.5cm}
\newcommand{\ie}{\emph{i.e.,}\xspace}
\newcommand{\eg}{\emph{e.g.,}\xspace}
\newcommand{\wrt}{\emph{w.r.t.}\xspace}
\newcommand{\aka}{\emph{a.k.a.}\xspace}
\newcommand{\kwlog}{\emph{w.l.o.g.}\xspace}
\newcommand{\etal}{\emph{et al.}\xspace}
\newcommand{\sstab}{\rule{0pt}{8pt}\\[-2.4ex]}

\begin{document}

Prof. xxx,\\
Editor-in-Chief,\\
IEEE International Conference on Data Engineering\\

@@

Dear Prof. xxx,

Attached please find a revised version of our submission to IEEE International Conference on Data Engineering, \emph{Query Independent Scholarly Article Ranking}.

The paper has been substantially revised according to the referees¡¯ comments. In particular, (1) we have further clarified our contributions, (2) we have explained the author component better, (3) we have added figures to show the statistics of data, (4) we have reported the memory cost in experience, (5) we have added related work of time delaying problem, and (6) we have also taken this opportunity to rewrite several parts of the paper to improve the presentation.

@@

The PeakMul pattern is defined in [19]:  the height of a peak should be at least 75\% of the maximum peak height, and two consecutive peaks should be separated by more than two years. In our work, we have simplified the pattern and only use the latest peak time which we have discussed in section II-A.

[19]  T. Chakraborty, S. Kumar, P. Goyal, N. Ganguly, and A. Mukherjee, ¡°On the categorization of scientific citation profiles in computer science,¡± Commun. ACM, vol. 58, no. 9, 2015.

\textbf{[R1D4]} \emph{For large scholar graph, such as MAG, it is better to use the distributed graph processing framework to improve the scalability of the method}

Yes, we agree that distributed processing is an important and independent problem which will be studied in future work and we have discussed it in Section VII Conclusion. Thanks for the suggestion!

@@

\textbf{[R2W2]} \emph{Presentation could improve a bit since the paper has too much notation making it hard to read/follow.}

Yes, we have gone over the paper and improved the presentation to make it more understandable. Thanks for the suggestion!

\textbf{[R2D1]} \emph{There seem to be two "contradictory" sides to this paper. From one side, this is a great "applications" paper where existing techniques and some good intuition is used to get better results into an existing (practical) problem. From a purely research and technical perspective, the paper is on the weak side. Pagerank and (incremental) versions of it already exist and the paper makes little contributions there. The claim (made twice) in the related work section that "Different from previous work" this paper focuses on citations statistics doesn't hold water. The fact that the authors are considering a different application domain is not a contribution compared to past (incremental) pagerank papers. Unless there is a better claim to be made about the algorithmic side of the paper, as things stand, the paper makes minimal technical contributions.}

We thank the reviewer for appreciating the practice merit of our work. And we believe this paper also stands from research and technique perspective. To our knowledge, the incremental algorithm of time-weighted PageRank has not gained enough attention and is lack of research. Furthermore, the exist incremental PageRank for dynamic scholarly article ranking which mentioned in [22] is based on a impractical assumption. Therefore, we have designed the incremental time-weighted PageRank algorithm for scholarly article ranking which has its unique features.  We have further clarified our contributions in Section I Introduction and claimed the technique difference of our algorithm in Section VI Related Work.

[22]  R. Ghosh, T. Kuo, C. Hsu, S. Lin, and K. Lerman, ¡°Time-aware ranking in dynamic citation networks,¡± in ICDM Workshops, 2011.

@@

\textbf{[R2D2]} \emph{The abstract starts with the sentence "Ranking query independent scholarly articles is a critical and challenging task, due to the heterogeneous, evolving and dynamic nature of entities involved in scholarly articles". If three types of data (articles, authors and venues) that are updated (maybe) weekly is considered challenging in terms of heterogeneity and dynamicity then one must wonder what one can say about real-life scenarios with thousands of data types where hundreds/thousands of new items are inserted daily (consider any online merchant system) and were ranking is important (recommendations). In summary, this sentence should go. Not to mention that the task is not really "critical".}

Yes, we have downgraded the tone and changed it into "practical and difficult". Thanks for the suggestion!

@@

\textbf{[R3W2\&D4]} \emph{The memory cost of the algorithms is better to be reported in the experiments.}

We have added the report of the memory cost in experiment Exp-x.x by numbers instead of figures due to the space limitation.Thanks for the suggestion!

\textbf{[R3D1]} \emph{Although the authors have a detailed introduction about the growing data, detailed figures about the data are recommended in the introduction.}

Yes, we have added a figure x to show the volume statistics of the data.

### 2017-12-24 icde/revision/sec-alg.tex

\stitle{Observation.} It is well-known that article citations obey a natural temporal order, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time. That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.

To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs (illustrated in Table~\ref{tab-batch}), where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}.
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs. In contrast, the \sccs in citation and venue graphs are quite small as a result of the temporal order of citations, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.

>>>>

\stitle{Observation.} It is well-known that article citations obey a natural {\em temporal order}, \ie an article only cites those published earlier, and it is really rare for the mutual citations between two articles published in the same time. That is, $|E_i|$ is essentially small for the citation graphs of scholarly articles.

To verify this observation, we also collect the statistics of citation graphs, venue graphs and Web graphs and illustrate in Table~\ref{tab-batch}, where Web graphs are extracted from berkely.edu and stanford.edu domains in 2002 and from the Google programming contest in 2002, respectively~\cite{LeskovecLDM09}, \markedb{and numbers $x/y$ in the first three rows are the corresponding statistics on citation/venue graphs.}
Due to the existence of the ``bow tie'' structure and the giant \scc in Web graphs~\cite{BroderKMRRSTW00}, the edge ratios $|E_i|/|E|$ are greater than 59\% for Web graphs. In contrast, the \sccs in citation and venue graphs are quite small as a result of the {\em temporal order of citations}, and $|E_i|/|E|$ is less than 3\% for all tested citation and venue graphs.
%
This specific structure in scholarly data has been long ignored in the past literature, which indeed has a positive impact on computations. Taking $t=100$ for example, algorithm \twprscc needs to scan $3|E|$ and $4|E|$ edges on citation and venue graphs, respectively, but over $59|E|$ edges on Web graphs.

### 2017-12-24 icde/revision/sec-intro.tex

Scholarly articles are involved with multiple entities such as authors, venues, dates and references. That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
However, effective and efficient ranking of nodes in such a large complex network is a challenging task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.

First, even if we are only to rank one type of entities (\ie scholarly articles), the other types of entities (\eg venues and authors) are closely involved, and, moreover, different types of entities may have different impacts on the ranking of scholarly articles.
%
Second, the importance of articles evolves with time in a complex manner~\cite{WangSB13,Chakraborty15}.
%Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, as researchers potentially have more interests in recently reported results. Indeed, as shown by the statistics of three scholarly datasets (\aan, \aminer and \magdata) in Fig.~\ref{fig-citation}, the citation numbers of articles in general reach the peak in the first 1 or 2 years after their publication, and then decrease accordingly. % Note that we do not plot the proportion of citations at $x=0$ on \aminer, which is an impractical value of 23.6\%. The above citation pattern is described as a complex log-normal probability in~\cite{WangSB13}.
Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, which conforms to the universal citation pattern of articles such that the number of citations generally grows in the first two to three years, and then declines in the following years~\cite{Chakraborty15}. In addition to the universal one, individual articles indeed follow a diverse set of patterns featured by the peak time of the number of citations~\cite{Chakraborty15}.
Finally, academic data is dynamic and continuously growing. Indeed, the number of articles in \magdata has exceeded 126 million, and keeps increasing at around 5.7 million per year~\cite{Sinha15:MAG}. This may cause certain long-term biases into data, \eg the number of citations increases significantly over time~\cite{BornmannM15}, which should be properly considered for scholarly article ranking.

Query independent ranking of scholarly articles remains challenging~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between articles published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.

>>>>

Scholarly articles are involved with multiple entities such as authors, venues, dates and references. That is, scholarly article ranking is essentially a problem of assessing the importance of nodes in a heterogeneous network.
However, effective and efficient ranking of nodes in such a large complex network is a different task due to the heterogeneous, evolving and dynamic natures of involved entities~\cite{AggarwalS14-survey,fcs-biggraph}.

First, even if we are only to rank one type of entities (\ie scholarly articles), the other types of entities (\eg venues and authors) are closely involved, and, moreover, different types of entities may have different impacts on the ranking of scholarly articles.
%
Second, the importance of articles evolves with time in a complex manner~\cite{WangSB13,Chakraborty15}.
%Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, as researchers potentially have more interests in recently reported results. Indeed, as shown by the statistics of three scholarly datasets (\aan, \aminer and \magdata) in Fig.~\ref{fig-citation}, the citation numbers of articles in general reach the peak in the first 1 or 2 years after their publication, and then decrease accordingly. % Note that we do not plot the proportion of citations at $x=0$ on \aminer, which is an impractical value of 23.6\%. The above citation pattern is described as a complex log-normal probability in~\cite{WangSB13}.
Newly published articles are very likely to have increasing impacts in the next few years, and those published many years ago tend to have decreasing impacts, which conforms to the universal citation pattern of articles such that the number of citations generally grows in the first two to three years, and then declines in the following years~\cite{Chakraborty15}. In addition to the universal one, individual articles indeed follow a diverse set of patterns featured by the peak time of the number of citations~\cite{Chakraborty15}.
Finally, academic data is dynamic and continuously growing. Indeed, the number of articles in Microsoft Academic Graph has exceeded 126 million, and keeps increasing at around 5.7 million per year~\cite{Sinha15:MAG}. This may cause certain long-term biases into data, \eg the number of citations increases significantly over time~\cite{BornmannM15}, which should be properly considered for scholarly article ranking.

Query independent ranking of scholarly articles remains difficult~\cite{wsdmcup}, although there exists quite a bit of work on scholarly article ranking, \eg~\cite{Garfield471,Liang16AAAI,Jiang12-MRank,Waltman2014}.
Most previous work exploits the time-dependent information of scholarly data in the form of exponential decay~\cite{Li08TSRanking,Wang13AAAI,sayyadi09,WalkerXKM07}, which fails to capture the diverse citation patterns of individual articles~\cite{Chakraborty15}.
Further, to our knowledge, little concern has been paid to dynamic scholarly article ranking except \cite{GhoshKHLL11} with a strong and impractical assumption that there are no citations between articles published in the same years.
%\marked{Finally, the bias caused by the dynamic nature of data has never been exploited in scholarly article ranking}.
